---
title: "Title of the Article"
author:
  - name: "Hector Martin"
  - name: "Pierrot Froment"
  - name: "AUdrey Heyraud"
abstract: >
  Abstract of the article.
date: "`r format(Sys.time(), '%d %B %Y')`"
url: https://github.com/Pie-Froment/soil_project
github-repo: GitHubID/Repository
lang: en-UK
otherlangs: [fr-FR,it]
bibliography: references.bib
biblio-style: chicago
preamble: >
  \hyphenation{bio-di-ver-si-ty sap-lings}
pdftoc: false
toc-depth: 3
urlcolor: blue
always_allow_html: yes
csquotes: true
output:
  bookdown::pdf_book:
    template: latex/template.tex
    citation_package: natbib
    latex_engine: xelatex
    keep_tex: true
  rmdformats::downcute:
    use_bookdown: yes
    lightbox: yes
  bookdown::gitbook:
    config:
      download: "pdf"
      sharing:
        github: yes
  bookdown::html_document2:
    toc: yes
    toc_float: yes
    css: style.css
    code_folding: show
  bookdown::word_document2: default
---

```{r}
#| label: DoNotModify
#| include: false
### Utilities. Do not modify.
# Installation of packages if necessary
InstallPackages <- function(Packages) {
  InstallPackage <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {
      install.packages(Package, repos = "https://cran.rstudio.com/")
    }
  }
  invisible(sapply(Packages, InstallPackage))
}

# Basic packages
InstallPackages(c("bookdown", "formatR", "kableExtra", "ragg"))

library("kableExtra")
library(bookdown)
library(formatR)
library(ragg)

# Chunk font size hook: allows size='small' or any valid Latex font size in chunk options
def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})
```

```{r Options, include=FALSE}
### Customized options for this document
# Add necessary packages here
Packages <- c("tidyverse")
# Install them
InstallPackages(Packages)

# knitr options
knitr::opts_chunk$set(
  cache =   FALSE,    # Cache chunk results
  include = TRUE,     # Show/Hide chunks
  echo =    TRUE,     # Show/Hide code
  warning = FALSE,    # Show/Hide warnings
  message = FALSE,    # Show/Hide messages
  # Figure alignment and size
  fig.align = 'center', out.width = '80%',
  # Graphic devices (ragg_png is better than standard png)
  dev = c("ragg_png", "pdf"),
  # Code chunk format
  tidy = TRUE, tidy.opts = list(blank=FALSE, width.cutoff = 50),
  size = "scriptsize", knitr.graphics.auto_pdf = TRUE
  )
options(width = 50)

# ggplot style
library("tidyverse")
theme_set(theme_bw())
theme_update(
  panel.background = element_rect(fill = "transparent", colour = NA),
  plot.background = element_rect(fill = "transparent", colour = NA)
)
knitr::opts_chunk$set(dev.args = list(bg = "transparent"))

# Random seed
set.seed(973)
```

# Introduction

# Method

## Study site

text, a document in different formats: HTML, LaTeX or Word for example.

## Sampling design

In RStudio, create a new document of type Document R Markdown. The wizard allows you to choose between different formats.

# Results

The main features of Markdown are summarized here.

## Wood decomposition

R code is included in code chunks:

## Tables

```{r}
#| label: kable
#| echo: true
#| warning: false
names(iris) <- c("Sepal length", "Width", "Petal length", "Width", "Species")
kableExtra::kbl(
  head(iris), 
  caption = "Table created by R", longtable = TRUE, booktabs = TRUE
  ) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

## Community composition

```{r}
#| label: pressure
#| fig-cap: "Figure title"
plot(pressure)
```

## PDF Document

The document is formatted according to the article LaTeX template.
